Handbook streamFind: Backend

### 2023-03-09 README.Rmd
Further text corrections

The streamFind project, entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle", is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and the [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The goal of the streamFind project is the development and assembly of data processing workflows for mass spectrometry and spectroscopy and the application of the workflows in environmental and quality studies of the water cycle. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind platform is directed to academics but also technicians, due to the aspired comprehensive documentation, well categorized set of integrated functions (or modules) and the graphical user interface (GUI).

@@

The [streamFind](https://github.com/ricardobachertdacunha/streamFind) back-end framework is an R package.

@@

For installation of the streamFind R package, it is recommended to first install the dependencies. Besides [R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only recommended for Windows users), the streamFind depends on the [patRoon](https://github.com/rickhelmus/patRoon) R package. The patRoon R package combines several tools for basic and advanced data processing and can be used interchangeably with the streamFind R package. The [handbook](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites) of the patRoon R package offers detailed installation instructions, including the list of mutually required [dependencies](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#other-dependencies).

Then, the streamFind R package can then be installed from the GitHub repository.

@@

The supplementary [streamFindData](https://github.com/ricardobachertdacunha/streamFindData) R package holds the data used in examples and other documentation assets of the streamFind R package and can be installed from the GitHub repository.

@@

The documentation and usage examples of the streamFind package can be found in the [reference page](https://ricardobachertdacunha.github.io/streamFind/reference/index.html) and [articles](https://ricardobachertdacunha.github.io/streamFind/articles/index.html) of the [webpage](https://ricardobachertdacunha.github.io/streamFind/index.html), respectively.

>>>>

The streamFind project, entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle", is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de), the [Forschungszentrum Informatik (FZI)](https://www.fzi.de/) and supporting partners. The goal of the streamFind project is the development and assembly of data processing workflows for mass spectrometry and spectroscopy and the application of the workflows in environmental and quality studies of the water cycle. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind platform is directed to academics but also technicians, due to the aspired comprehensive documentation, well categorized set of integrated modular functions and the graphical user interface. The streamFind development is ongoing, please [contact us](mailto:cunha@iuta.de) for questions  or collaboration.

@@

The back-end framework of [streamFind](https://github.com/ricardobachertdacunha/streamFind) is an R package.

@@

For installation of the streamFind R package, it is recommended to first install the dependencies. Besides [R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only recommended for Windows users), the streamFind depends on the [patRoon](https://github.com/rickhelmus/patRoon) R package and its dependencies. The patRoon R package combines several tools for basic and advanced data processing and can be used interchangeably with the streamFind R package. Installation instructions for patRoon and its dependencies can be found [here](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites).

Then, the streamFind R package can be installed from the GitHub repository.

@@

The supplementary [streamFindData](https://github.com/ricardobachertdacunha/streamFindData) R package holds the data used in examples and other documentation assets of the streamFind R package and can also be installed from the GitHub repository.

@@

The documentation and usage examples of the streamFind R package can be found in the [reference page](https://ricardobachertdacunha.github.io/streamFind/reference/index.html) and [articles](https://ricardobachertdacunha.github.io/streamFind/articles/index.html) of the [webpage](https://ricardobachertdacunha.github.io/streamFind/index.html).
